%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage{fontawesome}
\usepackage{hyperref}
% --> 1940 Westbury Avenue, Basement Suite, V2S1C1, Abbotsford, BC -> Abbotsford, BC, Canada
% -->66 Cornell Avenue Scarborough, Toronto -> Scarborough, Toronto, Canada
% 66 CORNELL AVE
% SCARBOROUGH ON   M1N 2Y2
% --> Saskatoon, Canada
% Set applicant's personal data for header
\name{Avijit Bhattacharjee}
\address{Saskatoon, Canada \linebreak
avb307@usask.ca \linebreak
(306) 713-9512}
\contacts{
\href{https://www.linkedin.com/in/avijit-bhattacharjee/}{ \underline{Linkedin}}

% \linebreak
\href{https://github.com/avijit1258}{ \underline{GitHub}}

\href{https://avijitbhattacharjee.com}{ \underline{Portfolio}}
}


\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{University of Saskatchewan}{}{Feb 2021 (expected)}
			\begin{itemize}
				\item \emph{M.Sc.} in Computer Science (Software Engineering) %, CGPA: 90.25\%
				% \item Graduate Coursework: Intelligent Systems Design; Automated Software Engineering; Human Driven Software Engineering for Scientific Workflow; Advanced Software Engineering.
				
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Khulna University}{}{ 2018}
			\begin{itemize}
				\item \emph{B.Sc.} in Computer Science \& Engineering
				% , CGPA: 3.74 / 4.0
				% \item Undergraduate Coursework: Artificial Intelligence; Pattern Recognition; Data Warehousing and Mining; Information Security and Control; Computer Graphics; Compiler Design; Digital Image Processing; Database Systems; Algorithms; Assembly Language.
				
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Employment}
     % 	 College of Education, USask
	    \begin{cvsubsection}{Software Engineer (part-time)}{}{Jan 2020 - Present}
	    \emph{Saskatchewan Education Leadership Unit}\\
	    Placement Application \href{https://placement.usask.ca}{\underline{link}}
    	    \begin{itemize}
    	        \item Upgraded web server from nginx to apache and modified codebase accordingly.
    	        \item Converted NoSQL based documents to MySQL based tables and migrated previous data to new MySQL based database.
    	        \item Structured development workflow by setting up independent development and production server.
    	        \item Fixed all deprecated functions in admin part due to change of database from NoSQL to MySQL based.
    	        \item Implemented secured forget password functionality.
    	        \item \textbf{Technologies} : Python, Flask, mongoDB, Apache, mariaDB, Linux, Git
    	         
    	        
    	    \end{itemize}
    	
    	\end{cvsubsection}
    	
    		\begin{cvsubsection}{Core CS Team Member (GWF)}{}{Jan 2019 - Present}
    		\emph{University of Saskatchewan}\\
    		Nutrient Application \href{https://gwf.usask.ca/projects-facilities/nutrient-app.php#Overview}{ \underline{link}}
    	    \begin{itemize}
    	        \item Developed REST API for 
    	        Nutrient Application to retrieve and store data in university owned database. 
    	        \item \textbf{Technologies} : Python, Flask, Postgres
    	        \item Implemented GEO map for the website of Nutrient app which shows Nitrate, Phosphate concentration at different Geo-location using the data from the REST API before-mentioned. \href{https://gwf.usask.ca/projects-facilities/nutrient-app.php#ViewYourMeasurements}{\underline{link}}
    	        \item \textbf{Technologies} : HTML, CSS, Jquery, leafletjs
    	        
    	    \end{itemize}
    	
        \end{cvsubsection}
	
    	\begin{cvsubsection}{Software Engineer Intern}{}{Feb 2017}
    	\emph{Trustaira Bangladesh Limited}
    	    \begin{itemize}
    	        \item Implemented a prototype in order to analyze sentiment in Bangla language text written using English characters. \href{https://techfoxweb.wordpress.com/2017/07/24/banglish-sentiment-analysis/}{ \underline{link}}
    	        \item \textbf{Technologies} : Python, pyAvroPhonetic, TextBlob, vaderSentiment 
    	        
    	    \end{itemize}
    	
    	\end{cvsubsection}
    	
    
        
        % \begin{cvsubsection}{Graduate Teaching Assistant}{University of Saskatchewan}{Fall 2019--Present}
    	   % \begin{itemize}
    	   %     \item In fall 2019, I was marker of Introduction to Programming(Python) course. My duty was to grade assignments, midterm and final papers.
    	        
    	   % \end{itemize}
    	
        % \end{cvsubsection}
	
	
	
	\end{cvsection}
	
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
			 %   \item \textbf{Website for Margin Med} (2020).
			 %   Developed an responsive static website for Margin Med which is an startup company providing medical care for rural people. \texttt{Html, Css, Bootstrap} \href{https://marginmed.com/#}{\faExternalLink}
			 
			 \item \textbf{URL Shortener} (2021). Built a full stack JavaScript app which transforms a long URL to a short URL and redirects the short URL to the long URL. (Node.js, Express, MongoDB, Mongoose)
			 
			 \item \textbf{healthTrend} (2020). Developed a web application which analyzes tweets according to trending health topics and peoples sentiment toward the topic and provides summary. (Python, Flask, Twitter API, gensim, spaCy, NLP)
			 
			 \item \textbf{Exercise Tracker} (2020). Built a full stack JavaScript app where users can sign up, log exercises, query previous exercises with custom date range. (Node.js, Express, MongoDB, Mongoose) 
			 
			
    		  \item \textbf{Online Admission Test Registration System} (2017). 
    			Developed a web based application for admission test registration to get admission at Khulna University. (PHP , MySQL, JQuery, Bootstrap)
				
				% \item \textbf{PMS (Project Management Software Like Trello) } (2017). Developed a project management system like Trello which can be used by developers to add, update stories, assign tasks to others, change status in the dashboard and many other facilities.  \emph{Laravel, PHP, Html, Css, Javascript}
				
				% \item \textbf{PIGEON (Online Bus Ticket Booking System)} (2016). Developed a web application which can be used to manage ticket selling of Bus service providers. \emph{PHP, Laravel, Javascript, Html, Bootstrap}
				
				% \item \textbf{TouchTypeMaster (Touch typing learning tool for windows)} (2015). Built an windows based desktop application which will help users to practice touch typing by tracking progress, teasing tests and interactive feedbacks. C\#
				
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	
% 	\begin{cvsection}{Additional Experience and Awards}
% 		\begin{cvsubsection}{}{}{}	
% 			\begin{itemize}
% 				\item \textbf{Deans Merit Scholarship (2015 – 2018):} 
% 				This scholarship is provided to students of Khulna University who secure merit position in final exams.
% 				\item \textbf{Department Teaching Scholarship(2019-Present):} Receiving scholarship from CS department of University of Saskatchewan as Graduate teaching assistant.
% 			\end{itemize}
% 		\end{cvsubsection}
		
		
% 	\end{cvsection}
	\newpage
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Language: Python, Node.js, Java
				\item Frameworks: Flask, Express, Laravel, Bootstrap
				\item Others: Linux, MySQL, MongoDB
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{References}
		\begin{cvsubsection}{}{}{}	
			References are available upon request.
		\end{cvsubsection}
	\end{cvsection}
	
	
	
	
	
\end{document}
